{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
Second-round of editing has began.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems. This is primarily because most of
embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy, at least, two criteria: minimal, manual intervention
after deployment and small footprint of computing resource consumption
and on executable code, with the assumption of reasonably good
performance. To this end, in this paper, we propose an ensemble of the
kernelized correlation filters (KCF), we call {\it E}nKCF, for a
single-target object tracking. In particular, we developed a committee
of KCFs to specifically address the scale-change and dynamic maneuver
of the target over frames. In addition, we devised a Bayes filter for
a smooth transition between individual KCFs' executions. Also, we
slightly modify the {\it E}nKCF to perform tracking in low frame rate
videos dominated by large ego-motion.  large ego-motion. Experimental
results showed that the performance of ours are 70.10\% for precision
on 20 pixels and 53.00\% for success rate for OTB100 data, and 54.50\%
and 40.2\% for UAV123 data. These results confirmed that our method
outperformed the existing ones over 5\% on precision on 20 pixels and
10-20\% on AUC on average. Our implementation ran at 340 fps for
OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
fps) for OTB100 and KCF (292 fps), DCF (457 fps) for UAV123.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\begin{comment}
\begin{itemize}
\item YoungWoo: Clean up the introduction
\item Burak: Clean up the technical section: EnKCF, KCF, and Particle Filter
\item Burak: You'll have a conclusion whether we'll have the re-detection part by Friday night.
\item By Monday, we'll have a draft ready to submit.
\end{itemize}
\end{comment}
A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deploying intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a lightweight or an array of monocular cameras. For
example, instead of having just bare flight function with video
recording, an unmanned air vehicle (UAV) equipped with an object or
feature following functionality would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

In this paper, we propose a single-target tracking aiming at running
on any embedded or mobile platforms that doesn't require an offline
training, and can run on an embedded system. In particular, we would
like to make our algorithm 1) learn the appearance model of a target
on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$Hz so that it could run, at least, faster than 30Hz when it
is deployed on a low-end, embedded system. With these features, our
tracking algorithm is ready to track an object of interest when it is
deployed on an embedded system. To this end, an online learning highly
efficient object tracking is more appropriate.

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can be easily implemented and run very efficiently
in an online fashion. In fact, a variant of the correlation filter,
the kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms, for example,
in VOT15 challenge, in terms of run-time and tracking
accuracy. However, the vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
primarily \cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
to the computational nature of correlation filter, however, this
approach would merely increase the computational complexity because it
has to run the correlation filter multiple times on each frame.

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large ($\leq0.5$, or $\geq2$).}
\label{ResultsIntroduction}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they use
the MOSSE tracker to estimate a target's translation. The scale is
updated in a way where the confidence map is used to determine the
scale change between successive frames. This is because they assume
the scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a
KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation in a highly efficient
manner.  In this paper, we use an ensemble of KCFs in turn, instead of
running them all together on every frame. By doing so, we could still
address the scale change and estimate target's motion efficiently
while increasing run-time performance. In particular, we deploy three
KCF in turn: \textit{target}+\textit{small background} translation
filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Fig.~\ref{fig:Filters} shows examples of the ROIs
associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
\begin{comment}
{\it We may not need this.}
The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
\end{comment}

@@

\item \textbf{Slight Modification of the proposed {\it E}nKCF for
  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
  the flexibility of the ensemble of KCFs approach we propose. The
  original {\it E}nKCF is slightly modified to track in low frame rate
  videos ($10$fps) dominated by large ego-motion. We do not integrate
  the particle filter in {\it E}nKCF2 as we test it on a temporally
  down-sampled UAV123 dataset (UAV123$\_$10fps) including sequences
  with large ego-motion on a UAV platform. Particle Filter can be
  deployed in case the camera motion is known. The run-time
  performance decreases to $150$ fps, however, ratio of the video
  frame rate and run-time performance is similar to {\it E}nKCF. The
  proposed framework can be seen in fig.~\ref{Workflows}.
%\begin{figure*}[!t]
%\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
%\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
%\label{Workflow_figure_EnKCF}
%\end{figure*}
%\begin{figure*}[!h]
%\centering
%\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
%\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
%\label{Workflow_figure_EnKCF2}
%\end{figure*}

\begin{comment}

\item \textbf{Re-Detection} A target loss is inevitable in object
  tracking. To cope with this, we developed a new target, re-detection
  that reliably detects when to lose the target and effectively
  re-detect the lost target. {\it How we can show how good our
    re-detection method is?}

\item We build a highly efficient ($\geq300$ fps) scale adaptive
  multiple kernelized correlation filter based tracker that
  outperforms the original KCF implementation with fixed scale
  framework both in terms of accuracy and performance. The studies
  following the KCF improved the fixed scale framework by running
  detection on a number of candidate ROIs to figure out the new scale
  of the object after estimating the translation of the object. This
  approach adds additional complexity to the original KCF
  implementation and drags down the run-time performance from $300$
  fps to less than $100$ fps.

\item We propose a target re-detection module that can minimize the
  target loss due to the scale filter that learns the object model
  using only-object area. Also, the target re-detection step is
  required to handle severe occlusions, pose variations, illumination
  changes and fast motion.

\item Since our visual tracker mostly focuses on tracking objects from
  aerial moving platforms, we design a new robust target-to-camera
  distance estimation method. This way, a safe distance between the
  target and the camera-platform can be preserved.
\end{comment}

\end{itemize}

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%---------------------------------------------------------------------- 
In this paper, we extend the KCF in that multiple KCFs are deployed,
in turn, to address a target's scale change and dynamic maneuvers
while preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of KCF computation results in a
small-footprint, executable. Such a fast execution will facilitate to
deploy the proposed algorithm on any embedded systems.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications on embedded systems. This is primarily because most of
embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy, at least, two criteria: minimal, manual intervention
after deployment and small footprint of consuming computational
resources and on executable code, with the assumption of reasonably
good performance. To this end, in this paper, we propose an ensemble
of the kernelized correlation filters (KCF), we call {\it E}nKCF, for
the problem of a single-target object tracking. In particular, we
developed a committee of KCFs to specifically address the scale-change
and dynamic maneuver of the target over frames. In addition, we
devised a Bayes filter for a smooth transition between individual
KCFs' executions. Experimental results showed that the performance of
ours are 70.10\% for precision on 20 pixels and 53.00\% for success
rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. In other
words, these results showed that our method is better than existing
ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deploying intelligent
algorithms to any existing embedded and/or mobile platforms. Among
those technologies, computer vision algorithms are getting more
attentions primarily because payloads of those mobile platforms are
limited to carry any other sensors than a lightweight or an array of
monocular cameras. For example, instead of having just bare flight
function with video recording, an unmanned air vehicle (UAV) equipped
with an object or feature following functionality would make it more
useful in the application of monitoring/surveillance/surveying on
private properties/wild-life/crop, video recording on
sports/movies/events, many others.

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. In particular, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$Hz so that it could run, at least, faster than 30Hz when it
is deployed on a low-end, embedded system.\footnote{We empirically
  come up with this computation about an 1/10th scale down of
  computational resources from a typical PC to an embedded system.}

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, this
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can be easily implemented and run very efficiently
in an online fashion. In fact, a variant of the correlation filter,
the kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms, for example,
in VOT15 challenge, in terms of run-time and tracking
accuracy. However, a vanilla form of such an online tracker is prone
to drift, and fails to track a target over a long period of time
primarily \cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target by just having multiple
correlation filters running on each frame could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
to the computational nature of correlation filter, however, this
approach would merely increase the computational complexity because it
has to run the correlation filter multiple times on each frame.

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Examples of tracking results by the proposed method on the
  ``UAV123'' dataset. This ``UAV123'' dataset is challenging for
  object tracking as a target's scale is changed drastically with a
  few frames.}
\label{ResultsIntroduction}
\end{figure*}

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, they use the MOSSE tracker to estimate a target's
translation. And then they attemped to update the scale of the target
a way where the confidence map is used to determine the scale change
between successive frames. This is based on an assumption that the
scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To be more specific, a
KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation, but in a more efficient
way. To be more specific, we use an ensemble of KCFs in turn, instead
of running them all together on every frame. In particular, we deploy
three KCF in turn: \textit{target}+\textit{small background}
translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
($R_{s}$) and \textit{target}+\textit{large background} translation
filter ($R_{t}^{L}$). By doing so, we could still address the scale
change and estimate target's motion efficiently while increasing
run-time performance. Figure \ref{fig:Filters} shows examples of the
ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.

@@

\item \textbf{Slight Modification of the proposed {\it E}nKCF for
  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
  the flexibility of the ensemble of KCFs approach we propose. The
  original {\it E}nKCF is slightly modified to track in low frame rate
  videos ($10$fps) dominated by large ego-motion. We do not integrate
  the particle filter in {\it E}nKCF2 as we test it on a temporally
  down-sampled UAV123 dataset (UAV123$\_$10fps) including sequences
  with large ego-motion on a UAV platform. Particle Filter can be
  deployed in case the camera motion is known. The run-time
  performance decreases to $150$ fps, however, ratio of the video
  frame rate and run-time performance is similar to {\it E}nKCF. The
  proposed framework can be seen in fig.~\ref{Workflows}.
\end{itemize}

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%---------------------------------------------------------------------- 
In this paper, we extend the KCF in that three KCFs are deployed, in
turn, to address a target's scale change and dynamic maneuvers while
preserving the overall execution time very fast, i.e., $\ge$ 300
fps. The efficient nature of the KCF computation results in a
small-footprint, executable. Our design principle is, if we could
deploy these KCFs in an efficient way, that the proposed algorithm
could achieve a high, run-time performance while effectively
addressing the scale variation and dynamic maneuvers of a target.
